### 2024-11-30 paper-en.tex
Finalize introduction

% \newcounter{notice}[section]
% \newenvironment{notice}[1][]{\refstepcounter{notice}\par\medskip
%     \noindent \textbf{Замечание~\thenotice. #1} \rmfamily
% }
% {\medskip}

@@

@@

%% Проверить, что оно нигде дальше не используется
% \begin{definition}
%     Let $G$ be a metagraph with variable weights. The girth of $G$ is the maximum among all girths of r-extensions of $G$.
% \end{definition}

@@

%%% ^^^^^^^^^^

@@

% Становится полноценной теоремой, которую надо доказать

\begin{theorem}\label{theorem_cycle_expansion}

    Пусть $G'$ ~--- двудольный граф. Обозначим $\theta = \min\limits_{H \in \Phi(G')} \{ |H| \}$. Тогда существует набор весов дуг графа $G'$ такой, что для полученного метаграфа существовало расширение с обхватом больше или равным $2 \theta$.

Thus, to construct graphs with greater girths metagraphs with greater girths should be used. For example multiple arcs must be avoided because they cause cycles with length $2$ significantly limiting the girth of an r-extension.

>>>>

%%%%% TODO

% Заключение: 
% <"повторить" последний абзац введения>
% Планы на будущее: обобщить концепцию метаграфов для произвольных (не двудольных) графов

% Литература

% Разобрать комментарии по тексту

% Проверить буквы: чтобы не пересекались и что выбрали удачные

% Журнал: дискретная математика, шпрингер

@@

\section{Introduction}

Many modern algorithms of data encoding use bipartite graphs with specific properties for error correction during data transmission over noise channels, e.g. Low Density Parity Check Codes \cite{LDPC}.

Methods of construction for such bipartite graphs are divided in two main categories: methods, based on random permutations of different graphs, e.g. brute-force search \cite{bruteforce} of pseudo-random permutation of matrices \cite{gallager}; and structured methods which build graphs based on fixed predefined structure, e.g. methods that use protographs \cite{protographs}.

Protographs are Tanner graphs, typically with relatively small number of vertices. They serve as blueprints for constructing larger LDPC-codes. Larger graph is obtained by "copy-and-permutate" operation: first protograph is copied several times, after that endpoints of edges are swapped so that subgraphs become interconnected. The performance of the larger graph can be predicted by analyzing the protograph.

Parts in Tanner graph are called respectively subcode part and digit part. Digit vertices correspond to bits passed through the channel and subcode vertices to parity checks of adjacent variable vertices. LDPC Algorithm checks values of subcode vertices, and if the error is detected, recursively traverses adjacent vertices. Thus if error has occurred in vertex belonging to a cycle, it will accumulate when algorithm fully walks the cycle. Hence graphs without short cycles should be used.

In this article we propose a structural method for construction of bipartite graphs with any given girth by expanding metagraphs. The algorithm for selection of optimal weights for metagraphs is developed. Precise estimation of girth among all expansions of metagraph is given. Algorithm for iterative selection of metragraph structure is proposed.

@@

@@

@@

\textbf{Теорема.}

Let $G'$ be a bipartite graph, and $\theta = \min\limits_{H \in \Phi(G')} \{ |H| \}$. For graph $G'$, there exists a set of weights of its edges such that at least one of metagraph $G'$ expansions has girth $2 \theta$.

\begin{proof}

Consider set of cycles $C$ on metagraph $G'$ with length less then $2 \theta$ such that for each cycle $c \in C$ there exists an expansions of $G'$ on which $c$ corresponds to non-cycles only.

We can use Algorithms 1 and 2 to select weights $w$ and parameter $r$ such that all cycles from $C$ correspond to non-cycles on all expansions determined by pairs $(w, r)$. Thus we can consider only expansions, where cycles from $C$ are broken. Therefore, consider only cycles on metagraph which correspond to cycles on all expansions. Note that all expansions determined by pairs $(w, r)$ have similar girth. Therefore. we can consider the shortest of such cycles only.

If a cycle on metagraph corresponds to cycles on all expansions, then its characteristic is $0$ independent of the selected weights. Hence this cycle walks through each of its edges the same number of times in the opposite directions.

Path can not walk through the same edge twice in a row, so its structure consists of several cycles, which are glued in a vertex of degree $3$ or greater. This structure corresponds to $(\mu + \eta)$-graph possibly glued with some additional paths. The length of such a cycle is at least $2(|\mu| + |\eta|)$. By the previous theorem, its length is at most $2(|\mu| + |\eta|)$. Thus the length of such a cycle is precisely $2 \theta$.

\end{proof}

Note that to construct graph with great girth metagraph with small girths should not be used. For example parallel edges must be avoided because they cause cycles with length $2$ significantly limiting the girth of an r-extension.

### 2024-11-30 paper.tex
Finalize introduction

>>>>

Доли в графе Таннера называют информационной и проверочной. Вершины информационной доли соответствуют битам передаваемым через канал, а вершины проверочной доли соответствуют проверкам на чётность. Алгоритм LDPC в ходе декодирования проверяет чётность проверочных вершин и в случае ошибки рекурсивно обходит связанные с ней узлы. Таким образом, если ошибка передачи данных произошла на вершине цикла, она начнёт накапливаться при полном прохождении цикла алгоритмом, усложняя устранение помех. Следовательно, следует использовать графы без коротких циклов.
